The Anthropological Notation Ontology (ANNO): A core ontology for annotating human bones and deriving phenotypes

### 2023-05-30 paper.tex
Rename anno.bib to paper.bib. Add reference for topographical anatomy.

Apart from contextual information, most informative clues can be found directly on the bone.
As a result, anthropological work relies on human anatomy, particularly the skeletal system and further tissues of the musculoskeletal system to classify and describe and thus document bones, anatomical structures and diagnostic features within the overall framework of the skeleton in a comprehensive and transparent fashion (Quelle 5).\todo{Heuschkel unveröffentlichte Forschung}
By transferring the principle of Earth topography, it is possible to create a precise map of the human skeletal and musculoskeletal system's \enquote{terrain} (QUELLE 6).\todo{z.B. Beleg zur Topographie. KH: könnte man hier als Quelle die TA nehmen?}
Such a map contains visible anatomical surface structures as well as artificial objects such as measurement points or content-related or methodologically based classifications and boundaries.
These are unequivocally located by accurate and exhaustive definitions that in turn allow for their easy retrieval and moreover serve as a basis for the objective examination, for instance in the form of measurements(QUELLE 7).\todo{Heuschkel unveröffentlichte Forschung}
Therefore the focus of the first research stage in the development of ANNO was therefore on the creation and usage of such a map.

@@

\nocite{*}
\bibliographystyle{ios1}
\bibliography{anno}
\end{document}

>>>>

Apart from contextual information, most informative clues can be found directly on the bone.
As a result, anthropological work relies on human anatomy, particularly the skeletal system and further tissues of the musculoskeletal system to classify and describe and thus document bones, anatomical structures and diagnostic features within the overall framework of the skeleton in a comprehensive and transparent fashion (Quelle 5).\todo{Heuschkel unveröffentlichte Forschung}
By transferring the principle of Earth topography, it is possible to create a precise map of the human skeletal and musculoskeletal system's \enquote{terrain} (QUELLE 6).\citep{topo}
Such a map contains visible anatomical surface structures as well as artificial objects such as measurement points or content-related or methodologically based classifications and boundaries.
These are unequivocally located by accurate and exhaustive definitions that in turn allow for their easy retrieval and moreover serve as a basis for the objective examination, for instance in the form of measurements(QUELLE 7).\todo{Heuschkel unveröffentlichte Forschung}
Therefore the focus of the first research stage in the development of ANNO was therefore on the creation and usage of such a map.

@@

\nocite{*}
\bibliographystyle{ios1}
\bibliography{paper}
\end{document}
